### 2019-10-08 README.Rmd
added Q's to readme
updated readme with questions for Heike

- What names should I give to the diagnostic plots?
- Color themes for the paper?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

>>>>

- Completed: 
    - connected limeaid to my forked version of lime
    - added sine example and analysis of default LIME explanations to paper
    - started section on heatmap plot
- What do you think of my work on the methods section so far?
- Should we schedule my oral prelim, or should we keep waiting until I get closer to finishing the paper?
- What names should I give to the diagnostic plots?
- Color themes for the paper?
- Could you help me with the interpretation of the default LIME explanations?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

**Sandia**

- I had a phone interview with them
- Did you get an email from them for a reference?

**Graphics Group**

- treats for Yihui's talk?
